Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-01-12 manuscript/manuscript.Rmd
updated fig colors

@@

  geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, alpha=0.75, color="grey25")+

@@

  scale_fill_manual(values=c("darkgoldenrod1", "steelblue4"))+

@@

  scale_fill_manual(values=c("darkgoldenrod1", "steelblue4"), labels=c("Year effects", "No year effects"))+

>>>>

myCols <- c("#237DA4", "#7ECAD0")

@@

  geom_boxplot(aes(x=year, y=resids, fill=simtype), outlier.shape = 1, outlier.size = 0, color="grey25")+

@@

  scale_fill_manual(values=myCols)+

@@

  scale_fill_manual(values=myCols, labels=c("Year effects", "No year effects"))+
